\cvsection{Work Experience}
\begin{cventries}
{\normalsize
  
  \cventry
  {Software Engineering Intern}
  {D. E. Shaw India Private Limited}
  {Hyderabad, India}
  {May 2020 - June 2020}
  {
    \begin{cvitems}
      \item Built an attachment prediction system for the internal ticketing management system, DESFlow.
      \item Experimented with various keyword based and ML based algorithms and built a Machine Learning model using the
      combination of Naïve Bayes and Graham’s algorithm achieving 90\% precision, 59\% recall and 90\% accuracy.
      \item Improved the Graham’s algorithm and employed normalized keyword approach on top of the Machine Learning model
      to improve the recall to 67\% and precision to 91\%.
      \item Extended the solution to handle similar use cases like setting the due date and closing the request and also added the
      support for active learning for model to evolve over time.
      \vspace{2mm}
    \end{cvitems}
  }

  \cventry
  {Software Developer, Boost C++ Organization}
  {\href{https://gist.github.com/sarthak2007/e4cc8b1d5aad194030ba4bfa183a87ef}{Google Summer of Code}}
  {India}
  {May 2019 - Aug 2019}
  {
    \begin{cvitems}
      \item Integrated Boost.Units with the existing base coordinate system and restructured all the classes to make them compat-
      ible with Boost.Units to provide a robust astronomical coordinate system.
      \item Created the parser for binary table extension and ASCII table extension for FITS File system.
      \item Wrote unit tests using Boost Unit Test framework.
      \vspace{2mm}
    \end{cvitems}
  }
  
\cventry
  {Full Stack Developer Intern}
  {\href{https://github.com/sarthak2007/SOC}{Summer of Code, IIT Kanpur}}
  {IIT Kanpur}
  {May 2018 - July 2018}
  {
    \begin{cvitems}
      \item Developed a dynamic and scalable web application using LAMP stack from scratch as an initiative to improve the medical
      system by keeping track of records of patients and their medical history.
      \item Implemented various functionalities like doctor could add a patient, update its records, refer it to another doctor, etc.
      and patient could search for doctors and the labs in his area.
      \item Developed a question-answer platform for the medical system which had the functionality to filter the questions based
      on illness, search questions based on keywords, notifications for patients if their questions get answered, etc.
      \item Technologies and languages used: PHP, MYSQL, AJAX, HTML, Javascript, Microsoft Azure(for deployment).
      \vspace{2mm}
    \end{cvitems}
  }
}
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv.tex"
%%% End: