\cvsection{Projects}
\begin{cventries}
    
    \cventry
    {Course Project, Prof. Debadatta Mishra}
    {Building gemOS}
    {IIT Kanpur}
    {July 2019 - November 2019}
    {
      \begin{cvitems}
        \item {Implemented file system syscalls including open, write, pipe, etc.}
        \item {Implemented multi-level paging management for syscalls like mmap, munmap and mprotect.}
        \item {Implemented smart process creation for system calls like cfork and vfork by properly managing the processes.}
        \item {Designed a read-write lock and parallelized hash tables using multi-threading.}
      \end{cvitems}
    } 
    
    \cventry
    {Course Project, Prof. Purushottam Kar}
    {DCaptcha}
    {IIT Kanpur}
    {November 2019}
    {
      \begin{cvitems}
        \item {Built a CAPTCHA decoder using OpenCV for Image Preprocessing and Segmentation.}
        \item {Used PyTorch for building a CNN for character recognition after segmentation.}
      \end{cvitems}
    }
    
    \cventry
    {Course Project, Prof. Nisheeth Srivastava}
    {Address Book}
    {IIT Kanpur}
    {August 2019}
    {
      \begin{cvitems}
        \item {Built an address book for cricketers for storing their details and batting average using Bash scripting.}
        \item {Added the functionalities for add, update, search and remove the data.}
        \item{Also built a tool to scrape Indian ODI players' records from Cricinfo to populate the address book.}
      \end{cvitems}
    } 
    
    \cventry
    {Association for Computing Activities, Department of CSE, IIT Kanpur}
    {Basics of Reinforcement Learning}
    {IIT Kanpur}
    {Jan 2018 - March 2018}
    {
      \begin{cvitems}
        \item {Learned about Markov Decision Processes, Q-Learning and SARSA.}
        \item {Implemented Q-learning algorithm to find the shortest possible path to reach diagonally opposite corner in a rectangular grid with obstructions and zero knowledge of environment. }
      \end{cvitems}
    } 
  
\end{cventries}
