\cvsection{Work Experience and Projects}
\begin{cventries}
{\Large
  
  \cventry
  {Boost C++ Organization}
  {Google Summer of Code}
  {}
  {May 2019 - Present}
  {
    \begin{cvitems}
      \item Integrated Boost.Units with the existing base coordinate system and restructured all the classes to make them compatible with units to provide a robust astronomical coordinate system.\vspace{1mm}
      \item Created the parser for binary table extension and ASCII table extension for FITS File system.
        \vspace{1.0mm}
      \item Used Template Meta Programming in C++ to provide almost no runtime overhead and allow users to write scientifically infallible code by detecting all the errors at the compile time.
     
      \vspace{1mm}
        \ifdefined \ONEPAGE \else
      \item Technologies Used: DBus, C++, CUPS, Google Cloud Printing
        \fi
    \end{cvitems}
  }

\cventry
  {Summer of Code, Prof. Sandeep Shukla}
  {Full Stack Developer Intern}
  {}
  {May - July 2018}
  {
    \begin{cvitems}
      \item Developed a dynamic and interactive web application from scratch as an initiative to improve the medical system by keeping track of
records of patients and their history.\vspace{1mm}
      \item Developed a question-answer platform for medical system using PHP and MYSQL in the backend with frontend made using HTML and Javascript.
        \vspace{1mm}
      \item Technologies and languages used: PHP, MYSQL, AJAX, HTML, Javascript, Microsoft Azure.
      \vspace{1mm}
      \item Project sponsored by NUTANIX and UPSIDC
      \vspace{1mm}
        \ifdefined \ONEPAGE \else
      \item Technologies Used: DBus, C++, CUPS, Google Cloud Printing
        \fi
    \end{cvitems}
  }
  
  \cventry
  {Association for Computing Activities, Department of CSE, IIT Kanpur}
  {Basics of Reinforcement Learning}
  {}
  {Jan 2018 - Mar 2018}
  {
    \begin{cvitems}
      \item Learned about Markov Decision Processes, Q-Learning and SARSA.\vspace{1mm}
      \item Implemented Q-learning algorithm to find the shortest possible path to reach diagonally opposite corner in a square grid with blocked paths of no prior information.
        \vspace{1mm}
        \ifdefined \ONEPAGE \else
      \item Technologies Used: DBus, C++, CUPS, Google Cloud Printing
        \fi
    \end{cvitems}
  }
}
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv.tex"
%%% End: