\cvsection{Work Experience}
\begin{cventries}
    
    \cventry
    {SDE Intern, DESFlow}
    {D.E. Shaw India Private Limited}
    {Hyderabad, India}
    {April 2020 - June 2020}
    {
      \begin{cvitems}
        \item {Built an attachment prediction system for the internal ticketing management system, DESFlow.}
        \item {Experimented with various keyword based and ML based algorithms and built a Machine Learning model using the combination of Na\"{i}ve Bayes and Graham's algorithm and achieved 90\% precision, 59\% recall and 90\% accuracy.}
        \item{Improved the Graham's algorithm and employed normalized keyword approach on top of the Machine Learning model to improve the recall to 67\% and precision to 91\%.}
        \item{Extended the solution to handle similar use cases like setting the due date and closing the request and also added the support for active learning for model to evolve over time.}
      \end{cvitems}
    }
        
    \cventry
    {Software Developer, Boost C++}
    {Google Summer of Code}
    {India}
    {May 2019 - August 2019}
    {
      \begin{cvitems}
        \item {Integrated Boost.Units with the existing base coordinate system and restructured all the classes to make them compatible with units to provide a robust astronomical coordinate system.}
        \item {Created the parser for binary table extension and ASCII table extension for FITS File system.}
        \item{Used Template Meta Programming in C++ to provide almost no run-time overhead and allow users to write scientifically infallible code by detecting all the errors at the compile time.}
      \end{cvitems}
    }

  \cventry
    {Full Stack Developer, Under Prof. Sandeep Shukla}
    {Summer of Code, IIT Kanpur}
    {IIT Kanpur, India}
    {May 2018 - July 2018}
    {
      \begin{cvitems}
        \item {Developed a dynamic and scalable web application using LAMP stack from scratch as an initiative to improve the medical system by keeping track of records of patients and their medical history.}
        \item {Implemented various functionalities like doctor could add a patient, update its records, refer it to another doctor, etc. and patient could search for doctors and the labs in his area.}
        \item {Developed a question-answer platform for the medical
system which had the functionality to filter the questions based on illness, search questions based on keywords, notifications for patients if their questions get answered, etc.}
        \item{Technologies and languages used: PHP, MYSQL, AJAX, HTML, Javascript, Microsoft Azure(for deployment).}
        % \item{Used Microsoft Azure to deploy the web application.}
        % \item{Conducted by Nutanix and UPSIDC.}
        % \item {Project approached by Professor for implementing in Health Center of institute.}
      \end{cvitems}
    }
   
  
\end{cventries}